The K2 Bright Star Survey I: Methodology and Data Release

### 2019-06-26 paper/ms.tex
bedding edits

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
While the \kepler\ Mission was designed to look at tens of thousands of faint stars ($V \gtrsim 12$), brighter stars, which saturate the detector, are important because they can be and have been observed by other instruments at very high signal-to-noise ratio. By analyzing the unsaturated scattered-light `halo' around these stars, we can and do retrieve precise light curves of most of the brightest stars in \ktwo fields from Campaign~4 onwards. The halo method is highly agnostic about the cause and form of systematics and we show that it nevertheless it is effective at extracting light curves from both normal and saturated stars. The key methodology is to optimize the weights of a linear combination of pixel time series with respect to an objective function. We test a range of such objective functions, finding that \textit{lagged Total Variation}, a generalization of Total Variation, performs well on both saturated and unsaturated \ktwo targets. Applying this to the bright stars across the \ktwo Campaigns, this reveals stellar variability ubiquitously, including effects of stellar pulsation, rotation, and binarity. Here we describe our pipeline, and present a catalogue of the bright stars studied, with classifications and parametrizations of their variability and remarks on interesting objects. These light curves are publicly available as a High Level Science Product from the Mikulski Archive for Space Telescopes (MAST). \href{https://github.com/benjaminpope/k2halo}{\color{linkcolor}\faGithub} % git link shamelessly borrowed from Luger!
\end{abstract}

@@

% intro kepler
The \kepler Space Telescope was launched with a main goal of determining the frequency of Earth-sized planets around Solar-like stars \citep{2010sci...327..977b}, a goal which it has substantially achieved \citep[e.g.][]{2013ApJ...766...81F,2013PNAS..11019273P,2014ApJ...795...64F,2015ApJ...809....8B}. In order to explore these populations it was necessary to observe hundreds of thousands of stars, with the consequence that the \kepler exposure time and gain were set to optimally observe eleventh or twelfth-magnitude stars, while bright stars are saturated and intentionally avoided. In the two-wheeled revival as the \ktwo mission, the \kepler telescope observed a sequence of ecliptic-plane fields containing many more very-saturated stars \citep{2014PASP..126..398H}. While it is difficult to obtain precise light curves of these stars because of their saturation, they are some of the most-valuable targets to follow up with photon-hungry methods such as interferometry and high-resolution spectroscopy, and they typically have long histories of previous observations. Dedicated bright-star space photometry missions such as MOST \citep{most} and the BRITE-Constellation \citep{brite,brite2} use very small telescopes (15 and~20\,cm apertures respectively), and we would prefer to use much larger telescopes such as \kepler (0.95\,m) to obtain higher precision light curves.

>>>>

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
While the \kepler\ Mission was designed to look at tens of thousands of faint stars ($V \gtrsim 12$), brighter stars that saturated the detector are important because they can be and have been observed very accurately by other instruments. By analyzing the unsaturated scattered-light `halo' around these stars, we can and do retrieve precise light curves of most of the brightest stars in \ktwo fields from Campaign~4 onwards. The halo method is highly agnostic about the cause and form of systematics and we show that it nevertheless it is effective at extracting light curves from both normal and saturated stars. The key methodology is to optimize the weights of a linear combination of pixel time series with respect to an objective function. We test a range of such objective functions, finding that \textit{lagged Total Variation}, a generalization of Total Variation, performs well on both saturated and unsaturated \ktwo targets. Applying this to the bright stars across the \ktwo Campaigns reveals stellar variability ubiquitously, including effects of stellar pulsation, rotation, and binarity. We describe our pipeline and present a catalogue of the \textcolor{red}{N} bright stars, with classifications and parametrizations of their variability and remarks on interesting objects. These light curves are publicly available as a High Level Science Product from the Mikulski Archive for Space Telescopes (MAST). \href{https://github.com/benjaminpope/k2halo}{\color{linkcolor}\faGithub} % git link shamelessly borrowed from Luger!
\end{abstract}

@@

% intro kepler
The \kepler Space Telescope was launched with a main goal of determining the frequency of Earth-sized planets around Solar-like stars \citep{2010sci...327..977b}. In order to explore these populations it was necessary to observe hundreds of thousands of stars, with the consequence that the \kepler exposure time and gain were set to optimally observe eleventh or twelfth-magnitude stars, while bright stars are saturated and intentionally avoided. In the two-wheeled revival as the \ktwo mission, the \kepler telescope observed a sequence of ecliptic-plane fields containing many more very-saturated stars \citep{2014PASP..126..398H}. While it is difficult to obtain precise light curves of these stars because of their saturation, they are some of the most-valuable targets to follow up with photon-hungry methods such as interferometry and high-resolution spectroscopy, and they typically have long histories of previous observations. Dedicated bright-star space photometry missions such as MOST \citep{most} and the BRITE-Constellation \citep{brite,brite2} use very small telescopes (15 and~20\,cm apertures respectively), and we would prefer to use much larger telescopes such as \kepler (0.95\,m) to obtain higher precision light curves.
